### 2020-10-03 Thesis-Abstract.tex
Update abstract

The root of the conflict lies in cryptography's dual role as enabler of radical privacy and cornerstone of security. The
emergence of strong encryption triggered the first crypto war, and its proliferation is causing the second. In the face
of both polarized and conciliatory voices, I analyze strategies that do and do not work on wicked problems and promote
an iterative approach to the problem of encryption and EA. Along the way I illustrate the components of the debate in
argument maps and demonstrate the security risks with data flow diagrams, making clear distinctions for the separate
problems of EA for data in motion and data at rest.

>>>>

The root of the conflict lies in cryptography's dual role as enabler of unprecedented privacy and cornerstone of
security. The emergence of strong encryption triggered the first crypto war, and its proliferation is causing the
second. In response to both polarized and conciliatory voices, I will analyze strategies that do and do not work on
wicked problems and promote an iterative approach to the case of encryption and EA. Along the way I will illustrate the
components of the debate in argument maps and demonstrate the security risks with data flow diagrams, making clear
distinctions for the separate problems of EA for data in motion and data at rest.
